Rate Transfers with Polyhedral Surrogate Losses /\\ Surrogate Regret Bounds for Polyhedral Losses

### 2021-05-13 rates-neurips-21/rates.tex
pass over setting

\usepackage{amsmath,amsfonts,amssymb}

@@

\DeclareMathOperator{\E}{\mathbb{E}}  % expectation
\DeclareMathOperator*{\argmax}{arg\,max}
\DeclareMathOperator*{\argmin}{arg\,min}
\DeclareMathOperator*{\arginf}{arg\,inf}

\newcommand{\reals}{\mathbb{R}}
\newcommand{\simplex}{\Delta_\Y}

@@

\newcommand{\D}{\mathcal{D}}
\newcommand{\R}{\mathcal{R}}
\newcommand{\X}{\mathcal{X}}
\newcommand{\Y}{\mathcal{Y}}

\newcommand{\risk}[1]{\underline{#1}}
\newcommand{\inprod}[2]{\langle #1, #2 \rangle}%\mathrm{int}(#1)}
\newcommand{\toto}{\rightrightarrows}

@@

\paragraph{Target problems.}
We consider supervised machine learning problems where data points have features in $\X$ and labels in $\Y$, a finite space.
The \emph{target problem} is to learn a hypothesis mapping $\X$ to a finite \emph{report (or prediction) space} $\R$, possibly different from $\Y$.
For example, in classification with an abstain option, $\R = \Y \cup \{\bot\}$ where $\bot$ represents abstaining from choosing a label.
In a ranking problem, $\R$ is the set of all permutations of $\Y$.

@@

For example, in binary classification, the target problem is to predict a label from $\R = \Y = \{-1,+1\}$ with $0$-$1$ loss.
The surrogate prediction space is typically $\reals$ and common surrogate losses include hinge loss and logistic loss.
These surrogates are typically associated with the link $\psi(u) = \mathrm{sign}(u)$, which maps negative predictions to $-1$ and nonnegative predictions to $+1$.
In general, given a target problem, the question is how to design a ``good'' surrogate loss $L$ and link $\psi$.
We will address one aspect of this question in this paper.

>>>>

\usepackage{bbm}
\usepackage{amsmath,amsfonts,amssymb}

@@

\DeclareMathOperator*{\argmax}{arg\,max}
\DeclareMathOperator*{\argmin}{arg\,min}
\DeclareMathOperator*{\arginf}{arg\,inf}

\newcommand{\reals}{\mathbb{R}}
\newcommand{\posreals}{\reals_{>0}}%{\reals_{++}}
\newcommand{\dom}{\mathrm{dom}}
\newcommand{\defeq}{\doteq}%\vcentcolon=} % define equals

@@

\newcommand{\simplex}{\Delta_\Y}

% alphabetical order, by convention
\newcommand{\A}{\mathcal{A}}
\newcommand{\C}{\mathcal{C}}
\newcommand{\D}{\mathcal{D}}
\DeclareMathOperator{\E}{\mathbb{E}}  % expectation
%\newcommand{\E}{\mathbb{E}}
\newcommand{\F}{\mathcal{F}}
\newcommand{\I}{\mathcal{I}}
\newcommand{\N}{\mathcal{N}}
\renewcommand{\P}{\mathcal{P}}
\newcommand{\Q}{\mathcal{Q}}
\newcommand{\R}{\mathcal{R}}
\newcommand{\Sc}{\mathcal{S}}
\newcommand{\U}{\mathcal{U}}
\newcommand{\X}{\mathcal{X}}
\newcommand{\Y}{\mathcal{Y}}

\newcommand{\risk}[1]{\underline{#1}}
\newcommand{\inprod}[2]{\langle #1, #2 \rangle}%\mathrm{int}(#1)}
\newcommand{\inter}[1]{\mathring{#1}}%\mathrm{int}(#1)}
%\newcommand{\expectedv}[3]{\overline{#1}(#2,#3)}
\newcommand{\expectedv}[3]{\E_{Y\sim{#3}} {#1}(#2,Y)}
\newcommand{\toto}{\rightrightarrows}
\newcommand{\strip}{\mathrm{strip}}
\newcommand{\trim}{\mathrm{trim}}
\newcommand{\fplc}{finite-piecewise-linear and convex\xspace} %xspace for use in text
\newcommand{\conv}{\mathrm{conv}}
\newcommand{\indopp}{\bar{\mathbbm{1}}}
\newcommand{\ones}{\mathbbm{1}}
% \DeclarePairedDelimiter\ceil{\lceil}{\rceil}

\newcommand{\regret}[3]{R_{#1}(#2,#3)}

@@

\paragraph{Target problems.}
We consider supervised machine learning problems where data points have features in $\X$ and labels in $\Y$, a finite space.
The \emph{target problem} is to learn a hypothesis mapping $\X$ to a finite \emph{report (or prediction) space} $\R$, possibly different from $\Y$.
For example, standard binary classification has $\Y = \R = \{-1,+1\}$.
In classification with an abstain option, $\R = \Y \cup \{\bot\}$ where $\bot$ represents abstaining from choosing a label.
In a ranking problem, $\R$ is the set of all permutations of $\Y$.

@@

For example, in binary classification, the target problem is given by $0$-$1$ loss, $\ell(r)_y = \ones\{r\neq y\}$, with surrogate losses typically defined over $\reals$.
Common surrogate losses include hinge loss and logistic loss.
These surrogates are typically associated with the link $\psi(u) = \mathrm{sign}(u)$, which maps negative predictions to $-1$ and nonnegative predictions to $+1$.

\paragraph{Surrogate regret bounds.}
Given a target problem, we would like to design surrogates which efficiently solve it.
A standard tool to establish this efficiency is a \emph{surrogate regret bound}.
We define the \emph{regret} of a hypothesis $h: \X \to \reals^d$ as the expected loss relative to the best possible.
Formally, for a surrogate $L$, the regret of $h$ with respect to data distribution $\D$ is given by $R_L(h;\D) = E_{(X,Y)\sim\D} L(h(X), Y) - \inf_{h':\X\to\reals^d} E_{(X,Y)\sim\D} L(h'(X),Y)$, where the minimum is taken over all measurable functions.
(One may equivalently assume the Bayes optimal hypothesis is in the function class.)
The target regret of $h$ is thus $R_\ell(\psi\circ h;\D) = E_{(X,Y)\sim\D} \ell(\psi(h(X)), Y) - \inf_{h':\X\to\R} E_{(X,Y)\sim\D} \ell(h'(X),Y)$, where we recall that $\psi$ is the link function.

A surrogate regret bound answers the following question: if we can minimize the true surrogate regret at a rate $f(n)$, given $n$ data points, how fast does the corresponding hypothesis $h_n$ minimize the target regret?
Formally, a surrogate regret bound is given by a function $\zeta : \reals_+ \to \reals_+$, such that
\begin{equation}
  \label{eq:surrogate-regret-bound}
  \forall \D, \forall h:\X\to\reals^d, \quad R_\ell(\psi\circ h;\D) \leq \zeta(\, R_L(h;\D) \,)~.
\end{equation}
A minimal requirement is that $(L,\psi)$ is \emph{consistent} with $\ell$, meaning $\zeta$ is continuous at $0$ and satisfies $\zeta(0) = 0$.

Many works have tried to go beyond consistency and understand the lowest possible $\zeta$ for a given target and surrogate.
For example, it is known that $\zeta$ \raf{examples: logistic, exponential, and hinge}.
Some general bounds are known for classes of surrogates, e.g. \raf{refs}.
Lacking, however, is a general understanding of what $\zeta$ one can expect from a surrogates, especially for arbitrary target losses.

We give two main results to deepen this understanding.
The first is that polyhedral (piecewise-linear and convex) surrogates always yield \emph{linear} regret bounds.
\begin{theorem}

\end{theorem}
The second is that sufficiently convex and smooth losses (i.e., ``non-polyhedral'') require $\zeta(\epsilon) = \Omega(\sqrt{\epsilon})$.
\begin{theorem}

\end{theorem}

\raf{Paragraph on implication for rates here.  Maybe Huber example?}

\raf{\hrule}
\raf{OLD STUFF starting here}
